---
title: "Homework"
author: "Erik Luis Lanuza Oehlerich"
date: "7/12/2021"
output: html_document
---
# https://github.com/Digital-Methods-HASS/MapsWithLeaflet/commit/6590b5530582c471b94be9734a8bc28a36436d85
## Choose favorite backgrounds in:
# https://leaflet-extras.github.io/leaflet-providers/preview/
## beware that some need extra options specified

# First install libraries
```{r}
library(leaflet)
library(htmlwidgets)
library(tidyverse)
library(tidyverse)
library(googlesheets4)
library(leaflet)
```


# Task 1 
## Make a DANmap
###
```{r}
DANmap <- leaflet() %>% 
  setView(lng = 8.9044025, lat = 56.4263246, zoom = 5)
esri <- grep("^Esri", providers, value = TRUE)
for (provider in esri) {
  DANmap <- DANmap %>% addProviderTiles(provider, group = provider)
}

DANmap
```


# load the coordinates in the map and check: are any points missing? Why?
## no all the cordinates are still there

```{r}
gs4_deauth()
places <- read_sheet("https://docs.google.com/spreadsheets/d/1PlxsPElZML8LZKyXbqdAYeQCDIvDps2McZx1cTVWSzI/edit#gid=124710918",
                     col_types = "cccnncnc")

glimpse(places)
```
# lets make a map with popups
```{r}
leaflet() %>% 
  addTiles() %>% 
  addMarkers(lng = places$Longitude, 
             lat = places$Latitude,
             popup = places$Description)
```


# Task 2: Read in the googlesheet data you and your colleagues 
## populated with data into the DANmap object you created in Task 1.
# se below
# gs4_deauth()
# places <- read_sheet("https://docs.google.com/spreadsheets/d/1PlxsPElZML8LZKyXbqdAYeQCDIvDps#2McZx1cTVWSzI/edit#gid=124710918",
# col_types = "cccnncnc")
# glimpse(places)

# Task 3: Can you cluster the points in Leaflet? Google "clustering options in Leaflet"
## yes i can do that, by adding the line
## clusterOptions = markerClusterOptions(),
## see task 1 for the reading of it 

```{r}
DANmap %>% 
  leaflet() %>% 
  addTiles() %>% 
  addProviderTiles("Esri.WorldPhysical", group = "Physical") %>% 
  addProviderTiles("Esri.WorldImagery", group = "Aerial") %>% 
  addProviderTiles("MtbMap", group = "Geo") %>% 
  addLayersControl(
    baseGroups = c("CartoDB.DarkMatter","Aerial", "Physical","Geo"),
    options = layersControlOptions(collapsed = T)) %>%
  addMarkers( lng = places$Longitude,
              lat = places$Latitude,
              clusterOptions = markerClusterOptions(),
              popup = paste("<strong>Type: </strong>",places$Type,
                            "<br><strong>Descripition : </strong>",places$Description))
```



# Task 4: Look at the map and consider what it is good for and what not.
## The map with the clusteroption turned on is good for getting and overview
## the bad thing about the map is it when you hover you mouse over one marker it  
## sometimes triangulates the wrong area.


# Task 5: Find out how to display notes and classifications in the map.

## see the code in line or downbelow.

# popup = paste("<strong>Type: </strong>",places$Type,
# "<br><strong>Descripition : </strong>",places$Description))


